Data in R packages

### 2019-02-09 03b_R-data.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# TODO
# Can the raw numbers have the %s provided with them? Or perhaps we can refer to a table of results for this as well.
# A bit meta, but should we include metadata, data dictionary, README, for this data used in the paper?
# scales::percent(0.1)
# ------------------------------------------------------------------------------------------------------
```
